---
title: "Navigo - Agents"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load files

```{r cars}
nasa_tlx <- read.csv("../results/nasa_tlx.csv", stringsAsFactors = FALSE)
decision_points <- read.csv("../results/decision_points.csv", stringsAsFactors = FALSE)
post_trial <- read.csv("../results/post_trial.csv", stringsAsFactors = FALSE)
```

## RQ1.b: Workload - NASA TLX

### Pure Conditions

```{r pressure, echo=FALSE}
text_color = paletteer_d(ghibli, MarnieLight1)[2]

nasa_tlx %>% 
  select(subject, pd.total, po.total, pe.total) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = variable, y = value)) +
  geom_jitter(alpha = .7, width = .25, height = .25) + 
  aes(col = variable) +
  scale_color_discrete(guide = FALSE) + 
  geom_boxplot(aes(fill = variable), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  labs(title = "NASA TLX Scores for pure conditions",
       x = "",
       y = "NASA TLX Score") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

ggsave("../outputs/pure_tlx.png", width=8, height=5)
```

*PD Condition*

```{r}
hist(nasa_tlx$pd.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$pd.total), sd=sd(nasa_tlx$pd.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$pd.total)
```

PD scores are normally distributed. p-value is greater than 0.05 thus the null hypothesis that it is normally distributed is NOT rejected.

```{r}
shapiro.test(nasa_tlx$pd.total)
```

*PO Condition*

```{r}
hist(nasa_tlx$po.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$po.total), sd=sd(nasa_tlx$po.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$po.total)
```

PO scores are normally distributed. p-value is greater than 0.05 thus the null hypothesis that it is normally distributed is NOT rejected.

```{r}
shapiro.test(nasa_tlx$po.total)
```

*PE Condition*

```{r}
hist(nasa_tlx$pe.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$pe.total), sd=sd(nasa_tlx$pe.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$pe.total)
```

PE scores are normally distributed. p-value is greater than 0.05 thus the null hypothesis that it is normally distributed is NOT rejected.

```{r}
shapiro.test(nasa_tlx$pe.total)
```

#### Paired t-test

*Fisher's F Test*

_PD vs PO_
Variances are equal because p-value > 0.05 which does NOT reject the null hypothesis.

```{r}
var.test(nasa_tlx$pd.total, nasa_tlx$po.total)
var.test(nasa_tlx$po.total, nasa_tlx$pd.total)
```

_PD vs PE_
Variances are equal because p-value > 0.05 which does NOT reject the null hypothesis.

```{r}
var.test(nasa_tlx$pd.total, nasa_tlx$pe.total)
var.test(nasa_tlx$pe.total, nasa_tlx$pd.total)
```

_PO vs PE_
Variances are equal because p-value > 0.05 which does NOT reject the null hypothesis.

```{r}
var.test(nasa_tlx$po.total, nasa_tlx$pe.total)
var.test(nasa_tlx$pe.total, nasa_tlx$po.total)
```

*Student's Paired t-test*
* Workload for Pure Driver condition is significantly less than the workload for Pure Optimal condition
* Workload for Pure Driver condition is significantly less than the workload for Pure Explorer condition
* Workload for Pure Optimal condition is significantly greater than the workload for Pure Explorer condition

```{r}
t.test(nasa_tlx$pd.total, nasa_tlx$po.total, paired = TRUE, alternative = "less")
t.test(nasa_tlx$pd.total, nasa_tlx$pe.total, paired = TRUE, alternative = "less")
t.test(nasa_tlx$po.total, nasa_tlx$pe.total, paired = TRUE, alternative = "greater")
```

### Shapiro-Wilk's Normality Tests for other Conditions

*DO Condition*

```{r}
hist(nasa_tlx$do.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$do.total), sd=sd(nasa_tlx$do.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$do.total)
shapiro.test(nasa_tlx$do.total)
```

*DE Condition*

```{r}
hist(nasa_tlx$de.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$de.total), sd=sd(nasa_tlx$de.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$de.total)
shapiro.test(nasa_tlx$de.total)
```

*OD Condition*

```{r}
hist(nasa_tlx$od.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$od.total), sd=sd(nasa_tlx$od.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$od.total)
shapiro.test(nasa_tlx$od.total)
```

*OE Condition*

```{r}
hist(nasa_tlx$oe.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$oe.total), sd=sd(nasa_tlx$oe.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$oe.total)
shapiro.test(nasa_tlx$oe.total)
```

*ED Condition*

```{r}
hist(nasa_tlx$ed.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$ed.total), sd=sd(nasa_tlx$ed.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$ed.total)
shapiro.test(nasa_tlx$ed.total)
```

*EO Condition*

```{r}
hist(nasa_tlx$eo.total, col="red", xlim=c(1,100), prob=TRUE)
x <- seq(1,100,0.1)
curve(dnorm(x,mean=mean(nasa_tlx$eo.total), sd=sd(nasa_tlx$eo.total)), 1, 100, col="blue", add=TRUE)
stat.desc(nasa_tlx$eo.total)
shapiro.test(nasa_tlx$eo.total)
```

### Driver Model factorial conditions

```{r}
nasa_tlx %>% 
  select(subject, pd.total, do.total, de.total, od.total, ed.total) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = variable, y = value)) +
  geom_jitter(alpha = .7, width = .25, height = .25) + 
  aes(col = variable) +
  scale_color_brewer(palette = "Set2", guide = FALSE) + 
  geom_boxplot(aes(fill = variable), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  scale_fill_brewer(palette = "Set2", guide = FALSE) +
  labs(title = "NASA TLX Scores for Driver conditions",
       x = "",
       y = "NASA TLX Score") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

ggsave("../outputs/d_factorial_tlx.png", width=10, height=5)
```

#### Paired t-test

*Fisher's F Test*

```{r}
var.test(nasa_tlx$pd.total, nasa_tlx$do.total)
var.test(nasa_tlx$pd.total, nasa_tlx$de.total)
var.test(nasa_tlx$pd.total, nasa_tlx$od.total)
var.test(nasa_tlx$pd.total, nasa_tlx$ed.total)
```

*Student's Paired t-test*

```{r}
t.test(nasa_tlx$do.total, nasa_tlx$pd.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$de.total, nasa_tlx$pd.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$od.total, nasa_tlx$pd.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$ed.total, nasa_tlx$pd.total, paired = TRUE, alternative = "greater")

1.739e-07 < 0.001
0.01306 < 0.05
0.0004981 < 0.001
2.89e-05 < 0.001
```

### Explorer Conditions

```{r}
nasa_tlx %>% 
  select(subject, pe.total, ed.total, eo.total, de.total, oe.total) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = variable, y = value)) +
  geom_jitter(alpha = .7, width = .25, height = .25) + 
  aes(col = variable) +
  scale_color_discrete(guide = FALSE) + 
  geom_boxplot(aes(fill = variable), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  labs(title = "NASA TLX Scores for Explorer conditions",
       x = "",
       y = "NASA TLX Score") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

ggsave("../outputs/e_factorial_tlx.png", width=8, height=5)
```

#### Paired t-test

*Fisher's F Test*

```{r}
var.test(nasa_tlx$pe.total, nasa_tlx$ed.total)
var.test(nasa_tlx$pe.total, nasa_tlx$eo.total)
var.test(nasa_tlx$pe.total, nasa_tlx$de.total)
var.test(nasa_tlx$pe.total, nasa_tlx$oe.total)
```

*Student's Paired t-test*

```{r}
t.test(nasa_tlx$ed.total, nasa_tlx$pe.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$de.total, nasa_tlx$pe.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$oe.total, nasa_tlx$pe.total, paired = TRUE, alternative = "greater")
```

*Wilcoxon Signed-rank test*
* EO Condition has a significantly greater workload compared to the Pure E condition.

```{r}
wilcox.test(nasa_tlx$eo.total, nasa_tlx$pe.total, paired = TRUE, alternative = "greater")
```

### Optimal Conditions

```{r}
nasa_tlx %>% 
  select(subject, po.total, od.total, oe.total, do.total, eo.total) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = variable, y = value)) +
  geom_jitter(alpha = .7, width = .25, height = .25) + 
  aes(col = variable) +
  scale_color_discrete(guide = FALSE) + 
  geom_boxplot(aes(fill = variable), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  labs(title = "NASA TLX Scores for Optimal conditions",
       x = "",
       y = "NASA TLX Score") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

ggsave("../outputs/o_factorial_tlx.png", width=8, height=5)
```

#### Paired t-test

*Fisher's F Test*

```{r}
var.test(nasa_tlx$po.total, nasa_tlx$od.total)
var.test(nasa_tlx$po.total, nasa_tlx$oe.total)
var.test(nasa_tlx$po.total, nasa_tlx$do.total)
var.test(nasa_tlx$po.total, nasa_tlx$eo.total)
```

*Student's Paired t-test*
* The DO condition had a significantly greater workload than the Pure O condition.

```{r}
t.test(nasa_tlx$od.total, nasa_tlx$po.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$oe.total, nasa_tlx$po.total, paired = TRUE, alternative = "greater")
t.test(nasa_tlx$do.total, nasa_tlx$po.total, paired = TRUE, alternative = "greater")
```

*Wilcoxon Signed-rank test*
* EO Condition has a significantly greater workload compared to the Pure E condition.

```{r}
wilcox.test(nasa_tlx$eo.total, nasa_tlx$po.total, paired = TRUE, alternative = "greater")
```

## RQ1.c: Deviations

### Impact on Deviations

```{r}
decision_points %>% 
  select(subject, task, devratio) %>% 
  filter(devratio > 0) %>%
  mutate(task = factor(task, levels = c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO"))) %>% 
  ggplot(aes(x = task, y = devratio)) +
  geom_jitter(alpha = .7, width = .25, height = 0) + 
  aes(col = task) +
  scale_color_discrete(guide = FALSE) + 
  geom_boxplot(aes(fill = task), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  labs(title = "Deviation Ratio per Condition",
       subtitle = "Only included drives with >0 deviations",
       x = "",
       y = "Deviation Ratio") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

# ggsave("../outputs/devratio_per_condition_nozero.png", width=8, height=5)
```

Count number of participants that deviated per condition

```{r}
decision_points %>% 
  select(subject, task, devs) %>% 
  filter(devs > 0) %>% 
  group_by(task) %>% 
  count()
```

Count number of deviations per subject

```{r}
decision_points %>% 
  select(subject, task, devs) %>% 
  filter(devs > 0) %>% 
  group_by(subject) %>% 
  count()
```


*Shapiro-Wilk's Normality Test*

```{r}
devratio_wide <- decision_points %>% 
  select(subject, task, devratio) %>% 
  dcast(subject ~ task, value.var = "devratio")

hist(devratio_wide$PD, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$PD), sd=sd(devratio_wide$PD)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$PD)
shapiro.test(devratio_wide$PD)
```

_PO_

```{r}
hist(devratio_wide$PO, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$PO), sd=sd(devratio_wide$PO)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$PO)
shapiro.test(devratio_wide$PO)
```

_PE_

```{r}
hist(devratio_wide$PE, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$PE), sd=sd(devratio_wide$PE)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$PE)
shapiro.test(devratio_wide$PE)
```

_DO_

```{r}
hist(devratio_wide$DO, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$DO), sd=sd(devratio_wide$DO)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$DO)
shapiro.test(devratio_wide$DO)
```

_DE_

```{r}
hist(devratio_wide$DE, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$DE), sd=sd(devratio_wide$DE)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$DE)
shapiro.test(devratio_wide$DE)
```

_OD_

```{r}
hist(devratio_wide$OD, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$OD), sd=sd(devratio_wide$OD)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$OD)
shapiro.test(devratio_wide$OD)
```

_OE_

```{r}
hist(devratio_wide$OE, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$OE), sd=sd(devratio_wide$OE)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$OE)
shapiro.test(devratio_wide$OE)
```

_ED_

```{r}
hist(devratio_wide$ED, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$ED), sd=sd(devratio_wide$ED)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$ED)
shapiro.test(devratio_wide$ED)
```

_EO_

```{r}
hist(devratio_wide$EO, col="red", xlim=c(0,1), prob=TRUE)
x <- seq(0,1,0.1)
curve(dnorm(x,mean=mean(devratio_wide$EO), sd=sd(devratio_wide$EO)), 0, 1, col="blue", add=TRUE)
stat.desc(devratio_wide$EO)
shapiro.test(devratio_wide$EO)
```

*Fisher's F Test*

```{r}
var.test(devratio_wide$PD, devratio_wide$PO)
var.test(devratio_wide$PD, devratio_wide$PE)
var.test(devratio_wide$PO, devratio_wide$PE)
var.test(devratio_wide$PD, devratio_wide$DO)
var.test(devratio_wide$PD, devratio_wide$DE)
var.test(devratio_wide$PD, devratio_wide$OD)
var.test(devratio_wide$PD, devratio_wide$ED)
var.test(devratio_wide$PO, devratio_wide$OD)
var.test(devratio_wide$PO, devratio_wide$OE)
var.test(devratio_wide$PO, devratio_wide$DO)
var.test(devratio_wide$PO, devratio_wide$EO)
var.test(devratio_wide$PE, devratio_wide$ED)
var.test(devratio_wide$PE, devratio_wide$EO)
var.test(devratio_wide$PE, devratio_wide$DE)
var.test(devratio_wide$PE, devratio_wide$OE)
```

*Wilcoxon Test*

```{r}
wilcox.test(devratio_wide$PD, devratio_wide$DO, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PD, devratio_wide$DE, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PD, devratio_wide$OD, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PD, devratio_wide$ED, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PO, devratio_wide$OD, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PO, devratio_wide$OE, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PO, devratio_wide$DO, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PO, devratio_wide$EO, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PE, devratio_wide$ED, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PE, devratio_wide$EO, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PE, devratio_wide$DE, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$PE, devratio_wide$OE, paired = TRUE, alternative = "greater")
wilcox.test(devratio_wide$DO, devratio_wide$PO, paired = TRUE, alternative = "less")
wilcox.test(devratio_wide$OD, devratio_wide$PO, paired = TRUE, alternative = "less")
```


```{r}
decision_points %>% 
  select(subject, choice, devratio) %>% 
  # filter(devratio > 0.0) %>% 
  mutate(choice = factor(choice, levels = c("D", "O", "E", "N"))) %>% 
  ggplot(aes(x = choice, y = devratio)) +
  geom_jitter(alpha = .7, width = .25, height = 0) + 
  aes(col = choice) +
  scale_color_discrete(guide = FALSE) + 
  geom_boxplot(aes(fill = choice), colour = text_color, show.legend = FALSE, 
               outlier.shape = NA, alpha = 0.4) +
  labs(title = "Deviation Ratio per Choice",
       subtitle = "Only included drives with >0 deviations",
       x = "",
       y = "Deviation Ratio") +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```

## RQ1.a Impact on Choices

### Histogram of Choices

```{r}
decision_points %>% 
  select(subject, task, choice) %>% 
  mutate(task = factor(task, levels = c("PD", "OD", "ED", "PO", "DO", "EO", "PE", "DE", "OE"))) %>% 
  mutate(choice = factor(choice, levels = c("N", "E", "O", "D"))) %>% 
  group_by(task) %>% 
  ggplot(aes(x = choice)) +
  geom_bar(alpha = 0.8) +
  aes(fill = choice) +
  scale_fill_brewer(palette = "Set2", guide = FALSE) + 
  coord_flip() +
  facet_wrap(~task) +
  labs(title = "Choice per Condition",
       x = "",
       y = "") +
  theme_tufte(base_family = "Avenir", ticks = TRUE)

ggsave("../outputs/choice_per_condition.png", width=8, height=5)
```

### Task vs Choices

```{r}
decisions_wide <- decision_points %>% 
  select(subject, task, choice) %>% 
  mutate(task = factor(task, levels = c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO"))) %>% 
  mutate(choice = factor(choice, levels = c("N", "E", "O", "D"))) %>% 
  group_by(task, choice) %>% 
  count() %>% 
  dcast(choice ~ task, value.var = "n", fill = 0)

decisions_wide_task <- decision_points %>% 
  select(subject, task, choice) %>% 
  mutate(task = factor(task, levels = c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO"))) %>% 
  mutate(choice = factor(choice, levels = c("N", "E", "O", "D"))) %>% 
  group_by(task, choice) %>% 
  count() %>% 
  dcast(task ~ choice, value.var = "n", fill = 0)

choice_d <- c(30,18,14,10,22,0,2,12,0)
choice_o <- c(0,9,0,18,8,15,0,0,23)
choice_e <- c(0,0,16,1,0,15,25,18,7)
task_choice <- as.data.frame(rbind(choice_d, choice_o, choice_e))
names(task_choice) <- c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO")

task_pd <- c(0,0,30)
task_po <- c(1,18,10)
task_pe <- c(25,0,2)
task_do <- c(0,9,18)
task_de <- c(16,0,14)
task_od <- c(0,8,22)
task_oe <- c(15,15,0)
task_ed <- c(18,0,12)
task_eo <- c(7,23,0)
task_choice <- as.data.frame(rbind(task_pd, task_po, task_pe, task_do, task_de, task_od, task_oe, task_ed, task_eo))
names(task_choice) <- c("Explorer", "Optimal", "Driver")
row.names(task_choice) <- c("PD", "PO", "PE", "DO", "DE", "OD", "OE", "ED", "EO")

task_choice_chisq <- chisq.test(task_choice)
corrplot(task_choice_chisq$residuals, is.cor = FALSE)
```

### Scenario vs Choices

```{r}
scenario_choices_wide <- decision_points %>% 
  select(subject, task, choice) %>% 
  mutate(task = factor(task, levels = c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO"))) %>% 
  mutate(choice = factor(choice, levels = c("N", "E", "O", "D"))) %>% 
  mutate(scenario = case_when(task == "PD" ~ "Regular Day",
                              task == "OD" ~ "Regular Day",
                              task == "ED" ~ "Regular Day",
                              task == "PO" ~ "In a hurry",
                              task == "DO" ~ "In a hurry",
                              task == "EO" ~ "In a hurry",
                              task == "PE" ~ "Lots of time",
                              task == "DE" ~ "Lots of time",
                              task == "OE" ~ "Lots of time")) %>% 
  group_by(scenario, choice) %>% 
  count() %>% 
  dcast(scenario ~ choice, value.var = "n", fill = 0)

scene_d <- c(18,8,64)
scene_o <- c(8,50,28)
scene_e <- c(56,15,16)
scenario_choice <- as.data.frame(rbind(scene_d, scene_o, scene_e))
names(scenario_choice) <- c("Explorer", "Optimal", "Driver")
row.names(scenario_choice) <- c("Regular Day", "In a hurry", "Lots of time")

scenario_choice_chisq <- chisq.test(scenario_choice)
corrplot(scenario_choice_chisq$residuals, is.cor = FALSE)

decision_points %>% 
  select(subject, task, choice) %>% 
  mutate(task = factor(task, levels = c("PD", "DO", "DE", "PO", "OD", "OE", "PE", "ED", "EO"))) %>% 
  mutate(choice = factor(choice, levels = c("N", "E", "O", "D"))) %>% 
  mutate(scenario = case_when(task == "PD" ~ "Regular Day",
                              task == "OD" ~ "Regular Day",
                              task == "ED" ~ "Regular Day",
                              task == "PO" ~ "In a hurry",
                              task == "DO" ~ "In a hurry",
                              task == "EO" ~ "In a hurry",
                              task == "PE" ~ "Lots of time",
                              task == "DE" ~ "Lots of time",
                              task == "OE" ~ "Lots of time")) %>% 
  group_by(scenario, choice) %>% 
  ggplot(aes(x = choice)) +
  geom_bar(alpha = 0.8) +
  aes(fill = choice) +
  scale_fill_brewer(palette = "Set2", guide = FALSE) + 
  coord_flip() +
  facet_wrap(~scenario) +
  labs(title = "Choice per Scenario",
       x = "",
       y = "") +
  theme_tufte(base_family = "Avenir", ticks = TRUE)

# ggsave("../outputs/choice_per_scenario.png", width=8, height=5)
```


## RQ2: Confidence and Trust

### Confidence

```{r}
conf_freq_condition <- post_trial %>% 
  mutate(pd = pd.conf, po = po.conf, pe = pe.conf, do = do.conf, de = de.conf, od = od.conf, oe = oe.conf, ed = ed.conf, eo = eo.conf) %>% 
  select(subject, pd, do, de, po, od, oe, pe, ed, eo) %>%
  melt(id("subject")) %>% 
  group_by(variable, value) %>% 
  count()

post_trial %>% 
  mutate(pd = pd.conf, po = po.conf, pe = pe.conf, do = do.conf, de = de.conf, od = od.conf, oe = oe.conf, ed = ed.conf, eo = eo.conf) %>% 
  select(subject, pd, do, de, po, od, oe, pe, ed, eo) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = value)) +
  geom_bar() +
  aes(fill = variable) + 
  scale_fill_viridis_d(guide = FALSE) + 
  facet_wrap(~variable) +
  theme_tufte(base_family = "Avenir", ticks = FALSE)

# ggsave("../outputs/confidence_per_condition.png", width=8, height=5)
```

*Shapiro-Wilk's Test*

```{r}
stat.desc(post_trial$pd.conf)
shapiro.test(post_trial$pd.conf)
stat.desc(post_trial$po.conf)
shapiro.test(post_trial$po.conf)
stat.desc(post_trial$pe.conf)
shapiro.test(post_trial$pe.conf)
stat.desc(post_trial$od.conf)
shapiro.test(post_trial$od.conf)
stat.desc(post_trial$oe.conf)
shapiro.test(post_trial$oe.conf)
stat.desc(post_trial$do.conf)
shapiro.test(post_trial$do.conf)
stat.desc(post_trial$de.conf)
shapiro.test(post_trial$de.conf)
stat.desc(post_trial$ed.conf)
shapiro.test(post_trial$ed.conf)
stat.desc(post_trial$eo.conf)
shapiro.test(post_trial$eo.conf)
```

*Wilcoxon Signed-rank test*

```{r}
wilcox.test(post_trial$od.conf, post_trial$pd.conf, paired = TRUE)
wilcox.test(post_trial$ed.conf, post_trial$pd.conf, paired = TRUE)
wilcox.test(post_trial$do.conf, post_trial$po.conf, paired = TRUE)
wilcox.test(post_trial$eo.conf, post_trial$po.conf, paired = TRUE)
wilcox.test(post_trial$de.conf, post_trial$pe.conf, paired = TRUE)
wilcox.test(post_trial$oe.conf, post_trial$pe.conf, paired = TRUE)
```

*Confidence vs Choice*

```{r}
post_choices <- post_trial %>% 
  mutate(pd = pd.conf, po = po.conf, pe = pe.conf, do = do.conf, de = de.conf, od = od.conf, oe = oe.conf, ed = ed.conf, eo = eo.conf) %>% 
  select(subject, pd, do, de, po, od, oe, pe, ed, eo) %>% 
  melt(id("subject")) %>% 
  mutate(task = variable) %>% 
  mutate(confidence = value) %>% 
  select(subject, task, confidence) %>% 
  mutate(task = case_when(task == "pd" ~ "PD",
                          task == "po" ~ "PO",
                          task == "pe" ~ "PE",
                          task == "do" ~ "DO",
                          task == "de" ~ "DE",
                          task == "od" ~ "OD",
                          task == "oe" ~ "OE",
                          task == "ed" ~ "ED",
                          task == "eo" ~ "EO"))

decision_points %>% 
  left_join(post_choices) %>% 
  select(choice, confidence) %>% 
  group_by(choice, confidence) %>% 
  count() %>% 
  dcast(confidence ~ choice, value.var = "n", fill = 0) %>% 
  select(confidence, D, O, E)

choice_d <- c(2,4,5,16,17,19,45)
choice_o <- c(2,5,5,8,26,20,16)
choice_e <- c(0,4,2,9,8,20,30)

conf_1 <- c(2,0,2)
conf_2 <- c(4,4,5)
conf_3 <- c(5,2,5)
conf_4 <- c(16,9,8)
conf_5 <- c(17,8,26)
conf_6 <- c(19,20,20)
conf_7 <- c(45,30,16)
# choice_confidence <- as.data.frame(rbind(choice_d, choice_o, choice_e))
# names(choice_confidence) <- c("1", "2", "3", "4", "5", "6", "7")
# row.names(choice_confidence) <- c("Driver", "Explorer", "Optimal")
choice_confidence <- as.data.frame(rbind(conf_1, conf_2, conf_3, conf_4, conf_5, conf_6, conf_7))
names(choice_confidence) <- c("Driver", "Optimal", "Explorer")
row.names(choice_confidence) <- c("1", "2", "3", "4", "5", "6", "7")

choice_confidence_chisq <- chisq.test(choice_confidence)
corrplot(choice_confidence_chisq$residuals, is.cor = FALSE)

decision_points %>% 
  left_join(post_choices) %>% 
  mutate(scenario = case_when(task == "PD" ~ "Regular Day",
                              task == "OD" ~ "Regular Day",
                              task == "ED" ~ "Regular Day",
                              task == "PO" ~ "In a hurry",
                              task == "DO" ~ "In a hurry",
                              task == "EO" ~ "In a hurry",
                              task == "PE" ~ "Lots of time",
                              task == "DE" ~ "Lots of time",
                              task == "OE" ~ "Lots of time")) %>% 
  filter(scenario == "Regular Day") %>% 
  select(choice, confidence) %>% 
  ggplot(aes(x = confidence)) +
  geom_bar() +
  aes(fill = choice) + 
  scale_fill_viridis_d(guide = FALSE) + 
  facet_wrap(~choice) +
  coord_flip() +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```


### Trust

```{r}
post_trial %>% 
  mutate(pd = pd.trust, po = po.trust, pe = pe.trust, do = do.trust, de = de.trust, 
         od = od.trust, oe = oe.trust, ed = ed.trust, eo = eo.trust) %>% 
  select(subject, pd, do, de, po, od, oe, pe, ed, eo) %>% 
  melt(id("subject")) %>% 
  ggplot(aes(x = value)) +
  geom_bar() +
  aes(fill = variable) + 
  scale_fill_viridis_d(guide = FALSE) + 
  facet_wrap(~variable) +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```

*Wilcoxon Signed-rank test*

```{r}
stat.desc(post_trial$pd.conf)
wilcox.test(post_trial$od.trust, post_trial$pd.trust, paired = TRUE)
wilcox.test(post_trial$ed.trust, post_trial$pd.trust, paired = TRUE)
wilcox.test(post_trial$do.trust, post_trial$po.trust, paired = TRUE)
wilcox.test(post_trial$eo.trust, post_trial$po.trust, paired = TRUE)
wilcox.test(post_trial$de.trust, post_trial$pe.trust, paired = TRUE)
wilcox.test(post_trial$oe.trust, post_trial$pe.trust, paired = TRUE)
```

*Correlation between Confidence and Trust*

```{r}
ggscatter(post_trial, x = "pd.conf", y = "pd.trust", 
          add = "reg.line",
          conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Confidence", ylab = "Trust")
```

```{r}
ggscatter(post_trial, x = "po.conf", y = "po.trust", 
          add = "reg.line",
          conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
          xlab = "Confidence", ylab = "Trust")
```


## RQ3: Detect Conversations


```{r}
post_trial %>% 
  filter(subject > 3) %>% 
  mutate(pd = pd.conv, po = po.conv, pe = pe.conv, do = do.conv, de = de.conv, 
         od = od.conv, oe = oe.conv, ed = ed.conv, eo = eo.conv) %>% 
  select(subject, pd, do, de, po, od, oe, pe, ed, eo) %>% 
  melt(id("subject")) %>% 
  mutate(value = case_when(value == 1 ~ "Yes",
                           value == 0 ~ "No")) %>% 
  ggplot(aes(x = value)) +
  geom_bar() +
  aes(fill = value) + 
  scale_fill_viridis_d(guide = FALSE) + 
  facet_wrap(~variable) +
  coord_flip() +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```

## RQ4: Familiarization vs Choice

### All conditions

```{r}
familiarization <- post_trial %>% 
  select(subject, f.good)

decision_points %>% 
  left_join(familiarization) %>% 
  select(subject, choice, f.good) %>% 
  filter(subject > 3) %>% 
  count(subject, choice, f.good) %>% 
  mutate(ratio_choice = ceiling((n/9)*100)) %>% 
  group_by(choice, f.good) %>% 
  summarize(mean_ratio_choice = mean(ratio_choice, na.rm = TRUE)) %>% 
  ggplot(aes(x = f.good, y = mean_ratio_choice)) +
  geom_col() +
  aes(fill = choice) +
  scale_fill_viridis_d(guide = FALSE) +
  facet_wrap(~choice) +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```

### Only conditions with D

```{r}
decision_points %>% 
  left_join(familiarization) %>% 
  filter(subject > 3) %>% 
  filter(agent1 == 'D' | agent2 == 'D') %>% 
  select(subject, choice, f.good) %>% 
  count(subject, choice, f.good) %>% 
  mutate(ratio_choice = ceiling((n/5)*100)) %>% 
  group_by(f.good, choice) %>% 
  summarize(mean_ratio_choice = mean(ratio_choice, na.rm = TRUE)) %>% 
  ggplot(aes(x = choice, y = mean_ratio_choice)) +
  geom_col() +
  aes(fill = choice) +
  scale_fill_viridis_d(guide = FALSE) +
  facet_wrap(~f.good) +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```

### Conditions with D scenarios

```{r}
decision_points %>% 
  left_join(familiarization) %>% 
  filter(subject > 3) %>% 
  filter(task == 'PD' | agent2 == 'D') %>% 
  select(subject, choice, f.good) %>% 
  count(subject, choice, f.good) %>% 
  mutate(ratio_choice = ceiling((n/3)*100)) %>% 
  group_by(f.good, choice) %>% 
  summarize(mean_ratio_choice = mean(ratio_choice, na.rm = TRUE)) %>% 
  ggplot(aes(x = choice, y = mean_ratio_choice)) +
  geom_col() +
  aes(fill = choice) +
  scale_fill_viridis_d(guide = FALSE) +
  facet_wrap(~f.good) +
  theme_tufte(base_family = "Avenir", ticks = FALSE)
```


